\documentclass[12pt]%, a4paper]
{article}
%\usepackage{geometry}
\usepackage{comment}
\usepackage[inner=1.5cm,outer=1.5cm,top=2.5cm,bottom=2.5cm]{geometry}
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}
\pagestyle{empty}

\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{fancyhdr, lastpage, bbding, pmboxdraw}
\usepackage[usenames,dvipsnames]{color}
\definecolor{darkblue}{rgb}{0,0,.6}
\definecolor{darkred}{rgb}{.7,0,0}
\definecolor{darkgreen}{rgb}{0,.6,0}
\definecolor{red}{rgb}{.98,0,0}
\usepackage[hyphens]{url}
\usepackage[colorlinks,pagebackref,pdfusetitle,urlcolor=darkblue,citecolor=darkblue,linkcolor=darkred,bookmarksnumbered,plainpages=false]{hyperref}
\usepackage[skins]{tcolorbox}
	\tcbset{colback=black!5}
	\tcbsetforeverylayer{colframe=yellow!50!black}
%\usepackage{texlogos}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\setlength{\parindent}{0pt}

\pagestyle{fancyplain}
\fancyhf{}
\lhead{ \fancyplain{}{MAT 130: Intro to Stats Spring 2024 Final Project Description} }
%\chead{ \fancyplain{}{} }
%\rhead{ \fancyplain{}{\textit{Last updated:} \today} }
%\rfoot{\fancyplain{}{page \thepage\ of \pageref{LastPage}}}
\fancyfoot[RO, LE] {page \thepage\ of \pageref{LastPage} }
\thispagestyle{plain}

%%%%%%%%%%%% LISTING %%%
\usepackage{listings}
\usepackage{caption}
\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\textwidth}{#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white}
\usepackage{verbatim} % used to display code
\usepackage{fancyvrb}
\usepackage{acronym}
\usepackage{amsthm}
\VerbatimFootnotes % Required, otherwise verbatim does not work in footnotes!


%\DeclareMathOperator{\Tor}{Tor}
%\DeclareMathOperator{\Ext}{Ext}

\definecolor{OliveGreen}{cmyk}{0.64,0,0.95,0.40}
\definecolor{CadetBlue}{cmyk}{0.62,0.57,0.23,0}
\definecolor{lightlightgray}{gray}{0.93}



\lstset{
%language=bash,                          % Code langugage
basicstyle=\ttfamily,                   % Code font, Examples: \footnotesize, \ttfamily
keywordstyle=\color{OliveGreen},        % Keywords font ('*' = uppercase)
commentstyle=\color{gray},              % Comments font
numbers=left,                           % Line nums position
numberstyle=\tiny,                      % Line-numbers fonts
stepnumber=1,                           % Step between two line-numbers
numbersep=5pt,                          % How far are line-numbers from code
backgroundcolor=\color{lightlightgray}, % Choose background color
frame=none,                             % A frame around the code
tabsize=2,                              % Default tab size
captionpos=t,                           % Caption-position = bottom
breaklines=true,                        % Automatic line breaking?
breakatwhitespace=false,                % Automatic breaks only at whitespace?
showspaces=false,                       % Dont make spaces visible
showtabs=false,                         % Dont make tabls visible
columns=flexible,                       % Column format
morekeywords={__global__, __device__},  % CUDA specific keywords
}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{center}
{\Large \textsc{Executive Summary}}
%\end{center}
%\begin{center}

\vspace{0.5pc}
118th Congress Project
%\end{center}
%\date{September 26, 2014}

\end{center}

\vspace{1.5pc}
This project uses logistic regression to predict whether a bill introduced in the 118th Congress will become a law.  

\vspace{0.5pc}
As of 1 June 2024, 15,366 bills have been introduced in the 118th Congress but only 64 have become law!  This means there is a severe class imbalance in the data.  To mitigate this, the algorithm was trained and used on four subsets of the data:
\begin{itemize}
\itemsep0em
\item All bills (15,366).
\item Bills that passed in the House (539).  Given that a bill passed in the House, will it become a law?
\item Bills that passed in the Senate (189).  Given that a bill passed in the Senate, will it become a law?
\item Bills that passed in both chambers (81).  Given that a bill passed in both chambers, will it become a law?
\end{itemize}

\vspace{0.5pc}
%\vfill
\begin{center}
{\large\textbf{Results}}
\end{center}  

\textbf{Train.}
\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{| l | c | c | c | c |}
\hline
\textbf{Trained on} & \textbf{Baseline Accuracy} & \textbf{Accuracy} & \textbf{Precision} & \textbf{Recall} \\
\hline
All bills & 99.6\% & 99.8\% & 100\% & 57.1\% \\
\hline
Passed in House & 90.7\% & 97.7\% & 80\% & 100\% \\
\hline
Passed in Senate & 66.7\% & 85.7\% & 83.3\% & 71.4\% \\
\hline 
Passed in both & 33.3\% & 83.3\% & 80\% & 100\% \\
\hline
\end{tabular}
\end{center}

\textbf{Test.}  We chose to test with the algorithm that was trained on the bills that passed in the House.  Here is how the model performed:

\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{| c | c | c | c |}
\hline
\textbf{Baseline Accuracy} & \textbf{Accuracy} & \textbf{Precision} & \textbf{Recall} \\
\hline
94.3\% & 97.7\% & 80\% & 57
1\% \\
\hline
\end{tabular}
\end{center}

\vspace{0.5pc}
\begin{center}
{\large\textbf{Implications}}
\end{center}

When training the KPIs looked pretty good, but when tested the model was likely overfit due to the severe class imbalance and due to the large number of features.  The next step is to work some more on dimension reduction and pinpoint which features lead to a bill becoming law.



\end{document} 